appendix

### 2023-01-28 paper_comparison/appendix.Rmd
update meeting note

Following the terminology introduced by @kullback1951information. $P$ represents the measured probability distribution, and $Q$ represents the assumed probability distribution. The Kullback-Leibler divergence is given as $\int_{-\infty}^{\infty}log(p(x)/q(x))p(x)dx$, where $p(.)$ and $q(.)$ denote probability densities of $P$ and $Q$.

>>>>

Following the terminology introduced by @kullback1951information, $P$ represents the measured probability distribution, and $Q$ represents the assumed probability distribution. The Kullback-Leibler divergence is defined as $\int_{-\infty}^{\infty}log(p(x)/q(x))p(x)dx$, where $p(.)$ and $q(.)$ denote probability densities of $P$ and $Q$.
